The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-11-14 borel-regularity.tex
Remove extra sentence; check spellings
Remove more commented-out draft text.

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
\end{enumerate}
\begin{center}
\basicLaplace
\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
\end{center}

@@

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which does not contain $0$, and may be displaced from $0$ by some distance $\Lambda$.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\renewcommand{\phase}{35}
\newcommand{\dis}{1.2}
\begin{fiber}[shade, phase=\phase, dis=\dis]
\genfibercontent[dual]
\draw (0, 0) -- (-\phase:\rshade);
\draw[rotate=-\phase] (\dis, -0.1) -- (\dis, 0.1);
\draw (0, 0) -- (0.75, 0);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\phase:0.5) node[midway, anchor=180-\phase/2] {$-\theta$};
\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{\phi}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over a constant-radius neighborhood of the ray $\zeta \in e^{i\theta}[0, \infty)$. 
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\radius}{0.85}
\begin{fiber}
\fill[pwbeige!30, draw=pwbeige!60, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
\genfibercontent
\draw (0, 0) -- (0.75, 0);
\draw[ray] (0, 0) -- (\phase:\rshade);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$\zeta$};
\end{fiber}
\end{tikzpicture}
\end{center}

The Watson--Nevanlinna--Sokal characterization of Borel regular functions is totally general, which means it cannot  take advantage of any extra structure provided by the problem you are trying to solve. We take the opposite approach, showing that certain functions are Borel regular just because of the extra structure provided by the problems they solve. 
%
\subsection{Solving level~$1$ ODEs}\label{sec:history_ODE}
%
The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones. Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behavior that changes sharply from from direction to the next. Formally, this behavior is captured in a {\em formal integral} solution: an expression
\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{F}_\alpha \]
in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$. For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.

@@

When $\zeta = 0$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_{\zeta, \alpha}^\theta \phi$ on $T_{\zeta = 0}^*B$, as long as we take care of a few subtleties. Thanks to the labeling choices we made in Section~\ref{sec:transl}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_{\zeta, \alpha}^\theta$. The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $\zeta = 0$, so we pull it back to $T^*_{\zeta = 0} B$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}. The inequality $\Re(e^{i\theta} z) > \Lambda$ cuts out a half-plane in $T_b^*B^{\otimes n}$, which pulls back to $n$ sector-like regions in $T_b^*B$ of angle $\pi/n$. We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.

@@

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,, \]
as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\begin{equation}\label{eqn:inverse-laplace-exp-bound}
\Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,.
\end{equation}
\begin{revised}To see why this bound holds, fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$. Consider the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, illustrated in Figure~\ref{fig:bound-real-part} for an extreme value of $\zeta_\alpha$.\end{revised}
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

@@

% point at node boundary
\begin{scope}[pwbeige!80!black]
\draw[out=170, in=25] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$} to (2.1, 1.7);
\draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
\end{scope}
\end{tikzpicture}
\captionof{figure}{\begin{revised}For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$. This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions actually require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.\end{revised} \begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}
\end{center}
\begin{revised}By construction, the curve $\mathcal{C}$ lies entirely outside this half-plane, which means that $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout $\mathcal{C}$. In fact, each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$. Therefore, as we move outward along $\mathcal{C}$, our distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at a rate of at least $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.\end{revised}

@@

If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$. The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega), \]
where $\mathcal{O}_{\zeta = \alpha}$ is the algebra of germs of holomorphic functions at $\zeta$. More generally, for any $\rho \ge \sigma$, the subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the $\rho$-shifted Taylor series exists can be seen as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega). \]

To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$. On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighborhood of $\zeta = 0$ in $\C$. Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[ietcoast!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[ietcoast!33] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[ietcoast!33!black] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
  \node[ietcoast!33!black] at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill[ietcoast!33!black] \p circle (0.7mm);
  }
\end{tikzpicture}
\captionof{figure}{The domain $\Upsilon$ at $\zeta=\alpha$.}\label{fig:domain_Upsilon}
\end{center}
For any $\sigma \in \R$, $\Lambda \in \R$, and non-integer $\rho \ge \sigma$, the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$. This operator is bounded, so its kernel is closed.
\end{proof}

@@

%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, does not touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.

@@

%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ does not contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ does not touch any other critical point (that is, does not contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}

@@

For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$. To prove Theorem~4 in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~3]{reg-sing-volterra}. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
and the perturbation
%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]

@@

Using the properties of the Borel tranform acting on trans-mononials \ref{sec:action_transseries} we get 
\begin{align*}
\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
\end{align*}
We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence. This ends the proof of part~\ref{part-2-prf}.

@@

We can distill the most interesting parts of the Airy-Lucas function by writing

@@

Starting from equation~\eqref{eqn:airy-distillation}, we can distill the most interesting part of the Airy function by writing

@@

where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.

@@

where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.

>>>>

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighbourhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
\end{enumerate}
\begin{center}
\basicLaplace
\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
\end{center}

@@

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which does not contain $0$, and may be displaced from $0$ by some distance $\Lambda$.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\renewcommand{\phase}{35}
\newcommand{\dis}{1.2}
\begin{fiber}[shade, phase=\phase, dis=\dis]
\genfibercontent[dual]
\draw (0, 0) -- (-\phase:\rshade);
\draw[rotate=-\phase] (\dis, -0.1) -- (\dis, 0.1);
\draw (0, 0) -- (0.75, 0);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\phase:0.5) node[midway, anchor=180-\phase/2] {$-\theta$};
\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{\phi}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over a constant-radius neighbourhood of the ray $\zeta \in e^{i\theta}[0, \infty)$. 
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\radius}{0.85}
\begin{fiber}
\fill[pwbeige!30, draw=pwbeige!60, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
\genfibercontent
\draw (0, 0) -- (0.75, 0);
\draw[ray] (0, 0) -- (\phase:\rshade);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$\zeta$};
\end{fiber}
\end{tikzpicture}
\end{center}

The Watson--Nevanlinna--Sokal characterization of Borel regular functions is totally general, which means it cannot  take advantage of any extra structure provided by the problem you are trying to solve. We take the opposite approach, showing that certain functions are Borel regular just because of the extra structure provided by the problems they solve. 
%
\subsection{Solving level~$1$ ODEs}\label{sec:history_ODE}
%
The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones. Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from from direction to the next. Formally, this behaviour is captured in a {\em formal integral} solution: an expression
\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{F}_\alpha \]
in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$. For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.

@@

When $\zeta = 0$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_{\zeta, \alpha}^\theta \phi$ on $T_{\zeta = 0}^*B$, as long as we take care of a few subtleties. Thanks to the labelling choices we made in Section~\ref{sec:transl}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_{\zeta, \alpha}^\theta$. The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $\zeta = 0$, so we pull it back to $T^*_{\zeta = 0} B$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}. The inequality $\Re(e^{i\theta} z) > \Lambda$ cuts out a half-plane in $T_b^*B^{\otimes n}$, which pulls back to $n$ sector-like regions in $T_b^*B$ of angle $\pi/n$. We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centred around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.

@@

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,, \]
as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\begin{equation}\label{eqn:inverse-laplace-exp-bound}
\Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,.
\end{equation}
To see why this bound holds, fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$. Consider the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, illustrated in Figure~\ref{fig:bound-real-part} for an extreme value of $\zeta_\alpha$.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

@@

% point at node boundary
\begin{scope}[pwbeige!80!black]
\draw[out=170, in=25] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$} to (2.1, 1.7);
\draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
\end{scope}
\end{tikzpicture}
\captionof{figure}{For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$. This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions actually require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$. \begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}
\end{center}
By construction, the curve $\mathcal{C}$ lies entirely outside this half-plane, which means that $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout $\mathcal{C}$. In fact, each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$. Therefore, as we move outward along $\mathcal{C}$, our distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at a rate of at least $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.

@@

If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighbourhood of $\zeta = 0$. The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega), \]
where $\mathcal{O}_{\zeta = \alpha}$ is the algebra of germs of holomorphic functions at $\zeta$. More generally, for any $\rho \ge \sigma$, the subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the $\rho$-shifted Taylor series exists can be seen as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega). \]

To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$. On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighbourhood of $\zeta = 0$ in $\C$. Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[ietcoast!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[ietcoast!33] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[ietcoast!33!black] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
  \node[ietcoast!33!black] at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill[ietcoast!33!black] \p circle (0.7mm);
  }
\end{tikzpicture}
\captionof{figure}{The domain $\Upsilon$ at $\zeta=\alpha$.}\label{fig:domain_Upsilon}
\end{center}
For any $\sigma \in \R$, $\Lambda \in \R$, and non-integer $\rho \ge \sigma$, the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counter-clockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighbourhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$. This operator is bounded, so its kernel is closed.
\end{proof}

@@

@@

@@

For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$. To prove Theorem~4 in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~3]{reg-sing-volterra}. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
and the perturbation
\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]

@@

Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries} we get 
\begin{align*}
\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
\end{align*}
We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence. This ends the proof of part~\ref{part-2-prf}.

@@

We can distil the most interesting parts of the Airy-Lucas function by writing

@@

Starting from equation~\eqref{eqn:airy-distillation}, we can distil the most interesting part of the Airy function by writing

@@

where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighbourhood of $z \in (-\infty, 0]$.

@@

where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighbourhood of $z \in [0, \infty)$.
